The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Update topic modeling part

@@

# Prepare document-term matrix as input for LDA model

# Reduce the size of the DTM by excluding words with a frequency lower than 5
emu_dtm <- convert_to_dtm(emu_words, 
                          title_col = "title", 
                          word_col = "word", 
                          min_term_freq = 5)

# Fit LDA model with K clusters
# # Determine K value empirically
# K = get_number_of_topics(emu_dtm)
# # This returns K = 23
# TODO run the model with K = 23 and compare with results using qualitative value

# Determine K value qualitatively
# K = 5 corresponds to the 2 TUD semesters and the 3 exchange semesters combined 
emu_lda <- LDA(emu_dtm, k = 5, method="Gibbs",
               control = list(seed = 2023, iter = 500, verbose = 25))

@@

# TODO Replace this with a table containing topics, documents, and theta
#      sorted by theta in decreasing order
# What is the dominant topic in each document?
N = 20
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- topic_names
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(rownames(topic_prop_examples))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")

>>>>

## Information extraction

@@

# Prepare document-term matrix as input for LDA model
# Reduce the size of the DTM by excluding words with a frequency lower than 5
emu_dtm <- convert_to_dtm(emu_words, 
                          title_col = "title", 
                          word_col = "word", 
                          min_term_freq = 5)

# Fit LDA model with K clusters
## Determine K value empirically
k = get_number_of_topics(emu_dtm)
# TODO run the model with the empirically determined k and compare (or combine) with results using qualitative value
emu_lda_k <- LDA(emu_dtm, k = k, method = "Gibbs",
               control = list(seed = 2023, iter = 500, verbose = 25))

## Determine K value qualitatively
## K = 5 corresponds to the 2 TUD semesters and the 3 exchange semesters combined 
emu_lda_5 <- LDA(emu_dtm, k = 5, method="Gibbs",
               control = list(seed = 2023, iter = 500, verbose = 25))

@@

# TODO Replace this with a table containing topics, documents, and theta
#      sorted by theta in decreasing order
# What is the dominant topic in each document?
N = 82
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- str_sub(topic_names, 1, 40)
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(str_sub(rownames(topic_prop_examples), 1, 20))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")

vizDataFrame |> 
  group_by(document) |> 
  mutate(value_max = max(value),
         topic_max = topic[value == value_max])
